PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
commit so I can push

# Specify cohort
```{r Specify cohort}
GLAD = FALSE
EDGI = TRUE
NBR = FALSE
RAMP = FALSE
```

@@

## Categorise age into groups 
In RAMP, age is indicated categorically: 16-18, 19-25, 26-35, 36-45, 46-55, 56-65, 66-70, 71-75, 76-80, 81-85, 86-90, 91-100, 100+
Age categories in GLAD, EDGI and NBR have been created to reflect this
```{r Age groups}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {
# Create categorical age groups per 10 years
dem.raw.id <- dem.raw.id %>%
  mutate(
    age_category_numeric =
      case_when(
          Age >= 16 & Age <= 18 ~ "1",
          Age >= 19 & Age <= 25 ~ "2",
          Age >= 26 & Age <= 35 ~ "3",
          Age >= 36 & Age <= 45 ~ "4",
          Age >= 46 & Age <= 55 ~ "5",
          Age >= 56 & Age <= 65 ~ "6",
          Age >= 66 & Age <= 70 ~ "7",
          Age >= 71 & Age <= 75 ~ "8",
          Age >= 76 & Age <= 80 ~ "9",
          Age >= 81 & Age <= 85 ~ "10",
          Age >= 86 & Age <= 90 ~ "11",
          Age >= 91 & Age <= 100 ~ "12",
          Age >= 101 & Age <= 120 ~ "13" # oldest person in the world is 117 years
                )
      )
}

@@

dem.raw.id %>%
  freq(age_category_full)

@@

  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
    mhd.depression = demographics.depression,
    mhd.pregnancy_depression = demographics.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
    mhd.agoraphobia = demographics.agoraphobia,
    mhd.panic_disorder = demographics.panic_disorder,
    mhd.panic_attacks = demographics.panic_attacks,
    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
    mhd.schizophrenia = demographics.schizophrenia,
    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
#    mhd.personality_disorder_diagnosed = demographics.personality_disorder_diagnosed, # does not exist in EDGI because it is multiple choice in EDGI
    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
    ) %>%
    add_column(
      mhd.schizoaffective_disorder = NA_character_
    ) %>%
    add_numeric(., exclude = exclude_cols_mhd2) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

nbr.mhd.raw.id <- nbr.mhd.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd."),
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
    mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa_unc = mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
    mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder
  ) %>%
  add_column(
    mhd.schizoaffective_disorder = NA #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
  ) %>% 
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r nbr mhd copy}
if(NBR == TRUE) {
  mhd.raw.id <- nbr.mhd.raw.id
}
```

@@

There is routing questionnaire if participants have been diagnosed with an eating disorder and afterwards they get asked the specific disorders. Therefore, mhd.suspected_eating_disorder_diagnosed_numeric needs to be recoded as 0 otherwise they would be NAs.
```{r nbr cleaning eating disorders}
if(NBR == TRUE) {
#Recode as 0 if ppt responds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    mhd.anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.atypical_anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bulimia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bingeeating_disorder_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bingeeating_disorder_unc_numeric == "0" ~ 0,
                mhd.bingeeating_disorder_unc_numeric == "1" ~ 1),
    mhd.anorexia_nervosa =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Anorexia nervosa",
                mhd.anorexia_nervosa_unc_numeric == "0" ~ "Not Anorexia nervosa",
                mhd.anorexia_nervosa_unc_numeric == "1" ~ "Anorexia nervosa"),
    mhd.atypical_anorexia_nervosa =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Atypical anorexia nervosa",
                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ "Not Atypical anorexia nervosa",
                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ "Atypical anorexia nervosa"),
    mhd.bulimia_nervosa =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Bulimia nervosa",
                mhd.bulimia_nervosa_unc_numeric == "0" ~ "Not Bulimia nervosa",
                mhd.bulimia_nervosa_unc_numeric == "1" ~ "Bulimia nervosa"),
    mhd.bingeeating_disorder =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Binge-eating disorder",
                mhd.bingeeating_disorder_unc_numeric == "0" ~ "Not Binge-eating disorder",
                mhd.bingeeating_disorder_unc_numeric == "1" ~ "Binge-eating disorder")
    )
}

@@

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders =
      recode_factor(obsessive_compulsive_disorders_numeric,
                    "0" = "No obsessive compulsive disorder",
                    "1" = "Obsessive compulsive disorder",
                    missing = NA_character_
                    )
  )

@@

  coping.nbr.gad.raw.id <- coping.nbr.gad.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(ID = as.numeric(ID)) %>% 
    select(
      Sample, # Sample
      ID, # ID
      startDate.coping = startDate, # Rename startDate
      gad.problems_made_difficult_care = gad.problems_made_care_difficult, # Impairment (different from GLAD)
      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
      gad.control_worrying_stop_retro = gad.control_worrying_stop,
      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
      gad.trouble_relaxing_retro = gad.trouble_relaxing,
      gad.sit_restless_hard_retro = gad.sit_restless_hard,
      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
      gad.awful_feeling_afraid_happen_retro = gad.feeling_afraid_awful_happen, #Different from GLAD
      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
      gad.awful_feeling_afraid_happen_base = gad.feeling_afraid_awful_happen.1 #Different from GLAD
    ) %>%
    add_numeric(., exclude = exclude_cols_coping_nbr) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r coping gad base sum score if missing items set to NA}
coping.gad.raw.id <- coping.gad.raw.id %>%
  mutate(
    gad.sum_score_base =
      if_else(condition = na_per_person_gad_base > 0,
              true = NA_real_,
              false = gad.sum_score_base_raw,
              missing = NA_real_
      )
  )

@@

```{r coping gad retro sum score if missing items set to NA}
coping.gad.raw.id <- coping.gad.raw.id %>%
  mutate(
    gad.sum_score_retro =
      if_else(condition = na_per_person_gad_retro > 0,
              true = NA_real_,
              false = gad.sum_score_retro_raw,
              missing = NA_real_
      )
  )

@@

```{r coping pcl base sum score if missing items set to NA}
coping.pcl.raw.id <- coping.pcl.raw.id %>%
  mutate(
    pcl.sum_score_base =
      if_else(condition = na_per_person_pcl_base > 0,
              true = NA_real_,
              false = pcl.sum_score_base_raw,
              missing = NA_real_
      )
  )

@@

```{r coping pcl retro sum score if missing items set to NA}
coping.pcl.raw.id <- coping.pcl.raw.id %>%
  mutate(
    pcl.sum_score_retro =
      if_else(condition = na_per_person_pcl_retro > 0,
              true = NA_real_,
              false = pcl.sum_score_retro_raw,
              missing = NA_real_
      )
  )

@@

```{r coping phq base sum score if missing items set to NA}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_base =
      if_else(condition = na_per_person_phq_base > 0,
              true = NA_real_,
              false = phq.sum_score_base_raw,
              missing = NA_real_
      )
  )

@@

8 items
```{r phq base sum score if missing items set to NA - 8 items}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_8items_base =
      if_else(condition = na_per_person_phq_base > 1 &
                phq.missing_only_suicide_item_base == 1,
              true = NA_real_,
              false = phq.sum_score_base_raw,
              missing = NA_real_
      )
  )

@@

```{r coping phq retro sum score if missing items set to NA}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_retro =
      if_else(condition = na_per_person_phq_retro > 0,
              true = NA_real_,
              false = phq.sum_score_retro_raw,
              missing = NA_real_
      )
  )

@@

8 items
```{r phq retro sum score if missing items set to NA - 8 items}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_8items_retro =
      if_else(condition = na_per_person_phq_retro > 1 &
                phq.missing_only_suicide_item_retro == 1,
              true = NA_real_,
              false = phq.sum_score_retro_raw,
              missing = NA_real_
      )
  )

@@

    ocir.repeat_feel_numbers_retro = ocir.repeat_numbers_feel, ## Different from GLAD
    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply,

@@

    ocir.light_switches_water_taps_retro = ocir.water_taps_light_switches, ## Different from GLAD

@@

    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel,
    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, 

@@

    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, 

@@

    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, 
    ocir.control_difficult_find_thoughts_retro = ocir.control_difficult_thoughts_find, ## Different from GLAD 
    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., 

@@

    ocir.repeat_feel_numbers_base = ocir.repeat_numbers_feel.1, ## Different from GLAD
    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1,

@@

    ocir.light_switches_water_taps_base = ocir.water_taps_light_switches.1, ## Different from GLAD

@@

    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, 
    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, 

@@

    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, 

@@

    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, 
    ocir.control_difficult_find_thoughts_base = ocir.control_difficult_thoughts_find.1,

>>>>

# Specify cohort
```{r Specify cohort}
GLAD = FALSE
EDGI = FALSE
NBR = FALSE
RAMP = TRUE
```

@@

## Categorise age into groups 
In RAMP, age is indicated categorically: 16-18, 19-25, 26-35, 36-45, 46-55, 56-65, 66-70, 71-75, 76-80, 81-85, 86-90, 91-100, 100+
Age categories in GLAD, EDGI and NBR have been created to reflect this
```{r Age groups}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
# Create categorical age groups per 10 years
dem.raw.id <- dem.raw.id %>%
  mutate(
    age_category_numeric =
      case_when(
          Age >= 16 & Age <= 18 ~ "1",
          Age >= 19 & Age <= 25 ~ "2",
          Age >= 26 & Age <= 35 ~ "3",
          Age >= 36 & Age <= 45 ~ "4",
          Age >= 46 & Age <= 55 ~ "5",
          Age >= 56 & Age <= 65 ~ "6",
          Age >= 66 & Age <= 70 ~ "7",
          Age >= 71 & Age <= 75 ~ "8",
          Age >= 76 & Age <= 80 ~ "9",
          Age >= 81 & Age <= 85 ~ "10",
          Age >= 86 & Age <= 90 ~ "11",
          Age >= 91 & Age <= 100 ~ "12",
          Age >= 101 & Age <= 120 ~ "13" # oldest person in the world is 117 years
                )
      )

@@

dem.raw.id %>%
  freq(age_category_full)
}
```

@@

  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
    mhd.depression = demographics.depression,
    mhd.pregnancy_depression = demographics.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
    mhd.agoraphobia = demographics.agoraphobia,
    mhd.panic_disorder = demographics.panic_disorder,
    mhd.panic_attacks = demographics.panic_attacks,
    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
    mhd.schizophrenia = demographics.schizophrenia,
    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
#    mhd.personality_disorder_diagnosed = demographics.personality_disorder_diagnosed, # does not exist in EDGI because it is multiple choice in EDGI
    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
    mhd.personality_disorder = demographics.personality_disorder,
    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder
    ) %>%
    add_column(
      mhd.schizoaffective_disorder = NA_character_
    ) %>%
    add_numeric(., exclude = exclude_cols_mhd2) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

nbr.mhd.raw.id <- nbr.mhd.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd."),
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
    mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa_unc = mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating_unc = mhd.psychological_overeating_or_bingeeating
  ) %>%
  add_column(
    mhd.schizoaffective_disorder = NA, #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
    mhd.schizoaffective_disorder_numeric = NA
  )
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r nbr mhd copy}
if(NBR == TRUE) {
  mhd.raw.id <- nbr.mhd.raw.id_renamed
}
```

@@

There is routing questionnaire if participants have been diagnosed with an eating disorder and afterwards they get asked the specific disorders. Therefore, mhd.suspected_eating_disorder_diagnosed_numeric needs to be recoded as 0 otherwise they would be NAs.
```{r nbr cleaning eating disorders}
if(NBR == TRUE) {
#Recode as 0 if ppt respnds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    mhd.anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.atypical_anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bulimia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bingeeating_disorder_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bingeeating_disorder_numeric == "0" ~ 0,
                mhd.bingeeating_disorder_numeric == "1" ~ 1)
    )
}

@@

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders =
      recode_factor(obsessive_compulsive_disorders_numeric,
                    "0" = "No obsessivecompulsive disorder",
                    "1" = "Obsessive compulsive disorder",
                    missing = NA_character_
                    )
  )

@@

  coping.nbr.gad.raw.id <- coping.nbr.gad.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(ID = as.numeric(ID)) %>% 
    select(
      Sample, # Sample
      ID, # ID
      startDate.coping = startDate, # Rename startDate
      gad.problems_made_difficult_care, # Impairment
      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
      gad.control_worrying_stop_retro = gad.control_worrying_stop,
      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
      gad.trouble_relaxing_retro = gad.trouble_relaxing,
      gad.sit_restless_hard_retro = gad.sit_restless_hard,
      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
    ) %>%
    add_numeric(., exclude = exclude_cols_coping_nbr) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r coping gad base sum score if missigng items set to NA}
coping.gad.raw.id <- coping.gad.raw.id %>%
  mutate(
    gad.sum_score_base =
      if_else(condition = na_per_person_gad_base > 0,
              true = NA_real_,
              false = gad.sum_score_base_raw,
              missing = NA_real_
      )
  )

@@

```{r coping gad retro sum score if missigng items set to NA}
coping.gad.raw.id <- coping.gad.raw.id %>%
  mutate(
    gad.sum_score_retro =
      if_else(condition = na_per_person_gad_retro > 0,
              true = NA_real_,
              false = gad.sum_score_retro_raw,
              missing = NA_real_
      )
  )

@@

```{r coping pcl base sum score if missigng items set to NA}
coping.pcl.raw.id <- coping.pcl.raw.id %>%
  mutate(
    pcl.sum_score_base =
      if_else(condition = na_per_person_pcl_base > 0,
              true = NA_real_,
              false = pcl.sum_score_base_raw,
              missing = NA_real_
      )
  )

@@

```{r coping pcl retro sum score if missigng items set to NA}
coping.pcl.raw.id <- coping.pcl.raw.id %>%
  mutate(
    pcl.sum_score_retro =
      if_else(condition = na_per_person_pcl_retro > 0,
              true = NA_real_,
              false = pcl.sum_score_retro_raw,
              missing = NA_real_
      )
  )

@@

```{r coping phq base sum score if missigng items set to NA}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_base =
      if_else(condition = na_per_person_phq_base > 0,
              true = NA_real_,
              false = phq.sum_score_base_raw,
              missing = NA_real_
      )
  )

@@

8 items
```{r phq base sum score if missigng items set to NA - 8 items}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_8items_base =
      if_else(condition = na_per_person_phq_base > 1 &
                phq.missing_only_suicide_item_base == 1,
              true = NA_real_,
              false = phq.sum_score_base_raw,
              missing = NA_real_
      )
  )

@@

```{r coping phq retro sum score if missigng items set to NA}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_retro =
      if_else(condition = na_per_person_phq_retro > 0,
              true = NA_real_,
              false = phq.sum_score_retro_raw,
              missing = NA_real_
      )
  )

@@

8 items
```{r phq retro sum score if missigng items set to NA - 8 items}
coping.phq.raw.id <- coping.phq.raw.id %>%
  mutate(
    phq.sum_score_8items_retro =
      if_else(condition = na_per_person_phq_retro > 1 &
                phq.missing_only_suicide_item_retro == 1,
              true = NA_real_,
              false = phq.sum_score_retro_raw,
              missing = NA_real_
      )
  )

@@

    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from NBR prepandemic
    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from NBR prepandemic

@@

@@

    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from NBR prepandemic
    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from NBR prepandemic

@@

    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from NBR prepandemic

@@

    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from NBR prepandemic
    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from NBR prepandemic
    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from NBR prepandemic

@@

    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from NBR prepandemic
    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from NBR prepandemic

@@

@@

    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from NBR prepandemic
    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from NBR prepandemic

@@

    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from NBR prepandemic

@@

    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from NBR prepandemic
    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from NBR prepandemic
